### 2014-11-13 tex/abstract.tex
abstract

A fundamental challenge of using symbolic execution for software
analysis has been the treatment of dynamically allocated data.
State-of-the-art techniques have addressed this challenge through
either (a) the use of summaries that over-approximate possible heaps, or
(b) by materializing a concrete heap lazily during generalized
symbolic execution. In this work, we present a novel heap
initialization and analysis technique which takes inspiration from
both approaches and constructs precise heap summaries lazily during
symbolic execution.  Our approach is 1) \emph{scalable}: it reduces the
points of non-determinism compared to generalized symbolic execution
and explores each control-flow path only once for any given set of
isomorphic heaps, 2) \emph{precise}: at any given point during symbolic
execution, the symbolic heap represents the exact set of feasible
concrete heap structures for the program under analysis, and 3)
\emph{expressive}: the symbolic heap can represent recursive data
structures. We demonstrate the precision and scalability of our
approach by implementing it as an extension to the Symbolic PathFinder
framework for analyzing Java programs.

>>>>

A fundamental challenge of using symbolic execution for software
analysis has been the treatment of dynamically allocated
data. Generalized symbolic execution (GSE) techniques have addressed
this challenge by materializing a concrete heap lazily during field
accesses.  This approach however, exacerbates the state space
explosion problem.  In this work, we present a novel symbolic
execution technique which takes inspiration from the static analysis
domain and defines a novel bipartite graph representation of the heap
and a lazy initialization algorithm that, unlike state-of-the-art
techniques, (a) supports aliasing, (b) does not require rewrite of
constraints on heap updates, (c) can initialize the heap-on-the-fly,
and (d) reduces the number of points of non-determinism during the
search. Our approach is sound and complete with respect to the
properties provable by GSE. A preliminary evaluation of our
implementation in Java Pathfinder shows the summary heap enables the
initialization of larger more complex heaps than previously possible.

\begin{comment}
A fundamental challenge of using symbolic execution for software
analysis has been the treatment of dynamically allocated data.
State-of-the-art techniques have addressed this challenge through
either (a) the use of summaries that over-approximate possible heaps, or
(b) by materializing a concrete heap lazily during generalized
symbolic execution. In this work, we present a novel heap
initialization and analysis technique which takes inspiration from
both approaches and constructs precise heap summaries lazily during
symbolic execution.  Our approach is 1) \emph{scalable}: it reduces the
points of non-determinism compared to generalized symbolic execution
and explores each control-flow path only once for any given set of
isomorphic heaps, 2) \emph{precise}: at any given point during symbolic
execution, the symbolic heap represents the exact set of feasible
concrete heap structures for the program under analysis, and 3)
\emph{expressive}: the symbolic heap can represent recursive data
structures. We demonstrate the precision and scalability of our
approach by implementing it as an extension to the Symbolic PathFinder
framework for analyzing Java programs.
\end{comment}
